KV Analysis for Non-Expressive performances

### 2021-02-01 material/expstimuli/analysis/stim_n/duration.Rmd
summarise data by subnr, trial
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r outlier, echo = FALSE}
excluded_duration <- duration[Mean < duration_all$Mean+3*duration_all$SD & Mean > duration_all$Mean-3*duration_all$SD]
print(excluded_duration)
```
- The number of excluded performance: `r duration_all$N-nrow(excluded_duration)`

>>>>

```{r outlier, echo = FALSE}
duration_trial <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr, TrialNr)]

excluded_duration <- duration_trial[Mean < duration_all$Mean+3*duration_all$SD & Mean > duration_all$Mean-3*duration_all$SD]
print(excluded_duration)
```
- The number of excluded performance: `r nrow(duration_trial)-nrow(excluded_duration)`

### 2021-02-01 material/expstimuli/analysis/stim_n/ioi_offset.Rmd
summarise data by subnr, trial
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```
- The number of excluded performance: `r ioi_all$N-nrow(excluded_ioi)`

>>>>

```{r outlier, echo = FALSE}
ioi_trial <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, TrialNr)]

excluded_ioi <- ioi_trial[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```
- The number of excluded performance: `r nrow(ioi_trial)-nrow(excluded_ioi)`

### 2021-02-01 material/expstimuli/analysis/stim_n/kv.Rmd
summarise data by subnr, trial
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r outlier, echo = FALSE}
excluded_kv <- kv[Mean < kv_all$Mean+3*kv_all$SD & Mean > kv_all$Mean-3*kv_all$SD]
print(excluded_kv)
```
- The number of excluded performance: `r kv_all$N-nrow(excluded_kv)`

>>>>

```{r outlier, echo = FALSE}
kv_trial <- dt_kv[EighthNote == "Yes", .(N = length(Velocity), Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, TrialNr)]

excluded_kv <- kv_trial[Mean < kv_all$Mean+3*kv_all$SD & Mean > kv_all$Mean-3*kv_all$SD]
print(excluded_kv)
```
- The number of excluded performance: `r nrow(kv_trial)-nrow(excluded_kv)`
